Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-08 Ben_Manuscripts/structure_paper/supporting_information.tex
Edits, organization, renamings, figure additions

\title{Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

@@

  \noindent
  \begingroup
	\fontsize{14pt}{14pt}\selectfont
	\textbf{Further details regarding monomer parameterization} 
  \endgroup

@@

  \noindent
  \begingroup
        \fontsize{14pt}{14pt}\selectfont
	\textbf{Calculation of pore-to-pore spacing statistics}
  \endgroup

  \vspace{1em}
  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\noindent \textbf{Experimental correlation length of R-$\pi$}
  \endgroup

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit paramaters. 
  % need citations and more on lorentzian parameters
  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\
  %Our model is insensitive to initial configuration if monomer placement is chosen within reason. 
  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Initial Configuration Dependence}
  \endgroup

@@

	  \item \underline{Initial pore spacing}

@@

	  \item \underline{Initial pore radius}

@@

	  \item \underline{Initial distance between layers}

@@

@@

>>>>

\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

@@

%  \noindent
%  \begingroup
%	\fontsize{14pt}{14pt}\selectfont
%	\textbf{Further details regarding monomer parameterization} 
%  \endgroup
  \section{Further details regarding monomer parameterization}\label{section:parameterization}

@@

  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.

  \section{Initial Configuration Dependence}\label{section:initial_config_dependence}
%  \begingroup
%	\fontsize{14pt}{12pt}\selectfont
%	\textbf{Initial Configuration Dependence}
%  \endgroup

@@

  %\begin{enumerate}

  %	  \item \underline{Initial pore spacing}
  \subsection{Initial pore spacing}\label{section:initial_pore_spacing}

@@

%	  \item \underline{Initial pore radius}
	  \subsection{Initial pore radius}\label{section:initial_pore_radius}

@@

%	  \item \underline{Initial distance between layers}
	  \subsection{Initial distance between layers}\label{section:initial_dbwl}

@@

%  \end{enumerate}

%  \noindent
%  \begingroup
%        \fontsize{14pt}{14pt}\selectfont
%	\textbf{Calculation of pore-to-pore spacing statistics}
%  \endgroup
  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}

%  \vspace{1em}
%  \begingroup
%	\fontsize{14pt}{12pt}\selectfont
%	\noindent \textbf{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
%  \endgroup

  \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}

  We calculated the nematic order parameter for our system in order to
  understand the degree of ordering among monomer head groups. Typically, the
  nematic order parameter is calculated for nematic liquid crystal systems which
  are characterized by unidirectional ordering of liquid crystal monomers. The
  preferred direction of monomers is defined by the unit director vector,
  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
  order parameter, $S$, is defined as:
  \begin{equation}
	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
	\label{eqn:nematic_order_parameter}
  \end{equation}
  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
  In a perfectly ordered system, the molecular axis should be aligned with
  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
  quantifying the degree of monomer head group alignment between systems. We use
  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
  the aromatic head groups.

  \section{Experimental correlation length of R-$\pi$}\label{section:correlation_length}

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit paramaters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on lorentzian parameters
  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  System & Diffusion Constant ($m^2/s$) \\ 
  \midrule
  Sandwiched, Ordered & $1.4\mathrm{e}{-14}$ \\
  Parallel Displaced, Ordered & $2.0\mathrm{e}{-14}$ \\
  Sandwiched, Disordered & $2.0\mathrm{e}{-14}$ \\
  Parallel Displaced, Disordered & $3.5\mathrm{e}{-14}$ \\
  \bottomrule
  \end{tabular}
  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
  which is three orders of magnitude lower than literature values.}~\label{table:msd}
  \end{table}
